\vspace{5em}On Evaluating Adversarial Robustness

### 2019-02-19 paper.tex
Adding Alex, addding explanation of list of contributors

\documentclass{article} % For LaTeX2e
\usepackage{iclr2019_conference}
\usepackage{natbib}
\usepackage{enumitem,amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{ifthen}
\usepackage{url}
%\usepackage{titling}
\usepackage{fancyhdr}

@@

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2019_conference}
\usepackage{natbib}
\usepackage{enumitem,amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{ifthen}
\usepackage{url}
%\usepackage{titling}
\usepackage{fancyhdr}
\usepackage{hyperref}

@@

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2},
  Alexey Kurakin\textsuperscript{1}\,\textsuperscript{*}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{*} List of authors is dynamic and subject to change.
  Authors are ordered according to the amount of their contribution
  to the text of the pape, similarly to how it's done in
  \href{https://github.com/tensorflow/cleverhans#authors}{Cleverhans tech report}
